### 2020-04-13 serial.tex
novel

Here, we provide an answer to the decade-old paradox.
We provide a new framework for understanding serial intervals and show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.

>>>>

Here, we provide an answer to this decade-old paradox.
We develop a novel framework for understanding serial intervals and show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
